\documentclass[11pt,a4paper]{article}

\usepackage[a4paper, top=0.5in, bottom=0.5in, left=0.75in, right=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{charter}
\usepackage[dvipsnames]{xcolor}
\usepackage{enumitem}

% ---------- colour ----------
\definecolor{hdr}{HTML}{1A5276}

% ---------- section header: title text followed by decorative rule ----------
\newcommand{\cvsection}[1]{%
  \vspace{0.5em}%
  \noindent{\Large\itshape\color{hdr}#1}%
  \hspace{0.4em}%
  {\color{hdr}\leavevmode\leaders\hrule height .55ex depth -.4ex \hfill\kern0pt}%
  \par\vspace{0.15em}%
}

% ---------- list style ----------
\setlist[itemize]{leftmargin=1.2em, topsep=2pt, itemsep=1pt, parsep=0pt}

% ---------- spacing ----------
\setlength{\parskip}{0pt}
\setlength{\parindent}{0pt}

% ---------- no page numbers ----------
\pagestyle{empty}

% ---------- helpers ----------
\newcommand{\entry}[4]{%
  \textbf{#1}\hfill#2\\
  \textit{#3}\hfill\textit{#4}\par\vspace{1pt}%
}
\newcommand{\proj}[2]{\textbf{#1}\hfill\textit{#2}\\}

% ==========================================================================
\begin{document}

% ---------- header ----------
{\LARGE\color{hdr}\textbf{C.T.}}\\[2pt]
{\itshape Software Engineer -- Python / Web}\\[2pt]
London, UK

% ---------- profile ----------
\cvsection{Profile}

Early-career software engineer focused on Python, web development, and
public-interest data. Founded an open-source civic technology project
making UK wealth inequality data accessible and interactive. DevOps and
Security Lead of a production-grade FastAPI platform with a 4-person
international team. At GE Digital, integrated automated security scanning
into $\sim$72 AWS CI/CD pipelines and learned a legacy Smallworld/Magik
codebase on the job. Published lead-author research in Springer
proceedings and present technical ideas to non-technical audiences through
university outreach work.

% ---------- experience ----------
\cvsection{Experience}

\entry{Open-Source Civic Technology Project}{2026 -- Present}
      {Founder \& Lead Developer}{London, UK}
\begin{itemize}
  \item Building open-source tools to make UK wealth inequality data
        accessible and impossible to ignore, with the goal of informing
        public understanding of tax policy and economic structures.
  \item Created a FastAPI backend with security headers, rate limiting,
        GZip compression, and CSV download; deployed via GitHub Actions
        with 8 CI/CD pipelines.
  \item Built 11 reproducible Python data pipelines ingesting ONS, HMRC,
        BoE, and WID government datasets, backed by a 40+ source
        open-data registry with full citations.
  \item Developing a policy microsimulation prototype to model the
        potential impact of UK tax reforms with provenance tracking.
  \item Built 72 Vue~3 components including 13 interactive chart
        visualisations with TailwindCSS, dark mode, and WCAG~AA
        accessibility; 1{,}235+ automated tests.
\end{itemize}

\entry{Collaborative Data Platform (pre-startup)}{2025 -- Present}
      {DevOps \& Security Lead}{Remote (international team)}
\begin{itemize}
  \item Architected a Python/FastAPI backend with 105 ORM models, 180
        database migrations, and 120+ REST API endpoints secured by
        JWT/RBAC auth gates, per-IP rate limiting, and Stripe billing.
  \item Led a security hardening sprint: identified and remediated
        6~CRITICAL + 13~HIGH vulnerabilities (SSRF, SQL injection, XFF
        spoofing, IDOR, brute-force) across 20 PRs with adversarial
        review.
  \item Built 39{,}500+ automated tests across a 4-tier framework
        (CI/validation/golden/nightly) with property-based testing
        (Hypothesis) and 125 golden-master scenarios.
  \item DevOps and Security Lead in a 4-person team, reviewing and
        merging 95\% of all pull requests across 640+ PRs and driving
        23 structured development phases.
\end{itemize}

\entry{Middlesex University}{Jun 2025 -- Present}
      {Outreach Contractor / Workshop Lead}{London, UK}
\begin{itemize}
  \item Deliver talks and workshops for schools and prospective students;
        regularly explain technical ideas to non-technical audiences and
        represent the university externally.
  \item Serve as the team's go-to data person (beyond the job
        description): data cleaning, visualisation, insight generation,
        and building automation scripts in Python.
  \item Contribute to a podcast initiative with secondary schools
        exploring societal pressures on young people; now developing a
        workshop programme bringing data literacy into schools.
\end{itemize}

\entry{GE Digital}{Jun 2023 -- Sep 2024}
      {Software Engineer Intern}{Cambridge, UK}
\begin{itemize}
  \item Integrated automated Nmap scanning into $\sim$72 AWS CI/CD
        pipelines in Jenkins using Bash and Groovy, reducing manual
        release checks and improving pre-release security coverage.
  \item Learned and maintained a legacy Smallworld/Magik codebase on the
        job (a language not previously encountered): fixed bugs, improved
        database interactions, added MUnit tests, and documented the
        system for onboarding.
  \item Worked with DevOps engineers and security architects on
        release-process hardening across a large enterprise environment.
  \item Received the GE Spotlight Award for ``Deliver with Focus'' for
        proactive ownership of a security-driven delivery initiative.
\end{itemize}

\entry{Middlesex University}{Apr 2025 -- Present}
      {Researcher \& Lead Author}{London, UK}
\begin{itemize}
  \item Led research on the N-Person Iterated Prisoner's Dilemma,
        building a Python simulation framework; published lead-author
        paper in Springer proceedings (SGAI-AI 2025) and presented as
        conference speaker.
\end{itemize}

% ---------- selected projects ----------
\cvsection{Selected Projects}

\proj{Taskdeck}{C\#, .NET~8, Vue~3, SQLite}
Local-first developer tool with proposal-first automation: every
AI-generated change produces a structured diff requiring explicit
approval before application. 188-endpoint REST API with real-time
SignalR, multi-provider LLM orchestration, and 8{,}600+ automated tests
with architecture-boundary enforcement at CI.

\medskip

\proj{N-Person Prisoner's Dilemma Research Platform}{Python}
Simulation and analysis framework for multi-agent cooperation research,
supporting experiments, visualisation, and publication-quality analysis.

\medskip

\proj{EduHub}{Vue.js, Node.js / Express, MongoDB}
Full-stack application for discovering and booking after-school lessons,
including search, filtering, cart/favourites flows, validation, and
RESTful APIs.

% ---------- education ----------
\cvsection{Education}

\entry{Middlesex University}{Graduated Jun 2025}
      {BSc (Hons) Computer Science with Industrial Placement, First Class
       Honours}{London, UK}

Relevant study included full-stack development, AI and algorithms, data
science and machine learning, software engineering, operating systems, and
computer networks.

% ---------- publication & awards ----------
\cvsection{Publication \& Awards}

Lead-author paper: ``Navigating the N-Person Prisoners' Dilemma: From the
Tragic Valley to the Collaborative Hill.'' \textit{Artificial Intelligence
XLII / SGAI-AI 2025}, Springer. Presenting conference speaker.

\medskip

\textbf{GE Spotlight Award -- Deliver with Focus} \hfill Dec 2023\\
Recognised for leading an essential DevSecOps initiative that integrated
automated port scanning into AWS-based CI/CD pipelines.

% ---------- leadership & service ----------
\cvsection{Leadership \& Service}

\entry{Middlesex University}{Nov 2024 -- Jul 2025}
      {Student Voice Leader \& Ambassador}{London, UK}
\begin{itemize}
  \item Gathered and presented student feedback to faculty and
        departmental boards; represented the university at information
        sessions, campus tours, and open-day activities.
\end{itemize}

% ---------- skills ----------
\cvsection{Skills}

\textbf{Languages:} Python, JavaScript, TypeScript, SQL, Bash, Groovy,
C\#, Java\\
\textbf{Backend / Web:} FastAPI, Node.js / Express, REST APIs, Vue~3,
React, HTML/CSS, TailwindCSS\\
\textbf{Infrastructure:} Docker, AWS, Jenkins, GitHub Actions, CI/CD,
Git, Linux\\
\textbf{Databases / Data:} PostgreSQL, MySQL, SQLite, MongoDB, Pandas,
scikit-learn\\
\textbf{Testing:} pytest, Vitest, Playwright E2E, Hypothesis
(property-based), MUnit\\
\textbf{Also:} Smallworld/Magik, D3.js, secure automation, OpenTelemetry

\end{document}
